### 2014-10-31 paper/include/refrint.tex
new version

For the hot rows, an approach similar to Smart Refresh is employed. The differences are that Refrint does not maintain a counter for each row, but a snapshot of a global counter as well as the row's valid bit. When a row is accessed, the corresponding snapshot is updated with the current value of the global counter. Whenever the global counter steps to a new value, all normal accesses are stalled and the logic checks whether any of the valid row's snapshot matches the global counter. If there is a match, a refresh is scheduled or the row is invalidated depending on the polices used for the cold rows.

@@

\todo[inline]{Drafty below. Ask Sally, confusing paper.}

Refrint modifies the MC and also stores data on chip(?). In an unmodified MC, there already exist a counter which can be used as the global counter and the authors have chosen to store the $N$ snapshot bits in the MC as well as the rows' valid bits in the MC. From experiments, the authors found out that one or two are good values for $N$. The logic to process the policies for the cold rows consists of decision logic, as well as Count bits and State bits for each cache row. This logic is located on chip(?)/in DRAM(?)(???) and has apparently a negligible overhead. In simulations, $N$ was two bits and Count was 5 bits, giving a total overhead of $0.6\%$, when cache row size is 64 bytes.

Presents the results. Add that we can not really use the result as they are from eDRAM.

>>>>

For the hot rows, an approach similar to Smart Refresh is employed. The differences are that Refrint does not maintain a counter for each row, but a snapshot of a global counter's highest bits as well as the row's valid bit. When a row is accessed, the corresponding snapshot is updated with the current value of the global counter. Whenever the global counter steps to a new value, all normal accesses are stalled and the logic checks whether any of the valid row's snapshot matches the global counter. If there is a match, a refresh is scheduled or the row is invalidated depending on the polices used for the cold rows.

@@

Refrint modifies the MC. The $N$ snapshot bits and a valid bit per DRAM row is stored in the MC and from experiments, Agrawal et al. found out that one or two are good values for $N$. To process the policies for the cold rows, decision logic as well as Count bits and State bits for each cache row is needed. Where the bits and logic resides is unclear to us, but they are placed outside the MC. In simulations, Agrawal et al. uses five Count bits, which give a negligible overhead and two bits for $N$. Of this, the total overhead became $0.005\%$, with a row size of \textit{8~KB}.

Results indicated that Refrint lower the total power consumption by $70\%$ but increases execution time of a cache hierarchy when evaluated as eDRAM, compared to an ordinary cache hierarchy using SRAM. Even though Refrint speeds up the execution time compared to an eDRAM hierarchy without Refrint, the execution time is increased by $6\%$  with respect to the SRAM solution, due to the characteristics of eDRAM.

### 2014-10-31 paper/include/smart_refresh.tex
new version

The counters are decremented in such a fashion so the refreshes are distributed evenly over time and thus avoiding burst refresh. To achive this, the counters are initially staggered and divided into n logical blocks where the counters are accessed in a sequential order. Only $n$ counters will be accessed, set or decremented at the same point in time, which result in that maximum $n$ rows are refreshed simultainously.

The counters bit size corresponds to the time granularity in where an access can be captured. A higher bit size results in that an access can be captured later in time, which effectively postpones the refresh further. The least optimal case for postponing the refresh is if the row access occurs a small time intervall before the counter is accessed. If a two-bit counter is used the least optimal row access result in that the row is refreshed after $3/4$ of the maximum refresh period. Analogously, a three-bit counter result in that a row is refreshed after minimum $7/8$ of the maximum refresh period.

@@

The technique was simulated on \textit{2~GB} of main memory. Result shows that the refresh reduction was in average $59\%$ and refresh power consumption savings was on average $52\%$, all without any performance degradation.

>>>>

The counters are decremented in such a fashion so the refreshes are distributed evenly over time and thus avoiding burst refresh. To achieve this, the counters are initially staggered and divided into n logical blocks where the counters are accessed in a sequential order. Only $n$ counters will be accessed, set or decremented at the same point in time, which result in that maximum $n$ rows are refreshed simultaneously.

The counters bit size corresponds to the time granularity in where an access can be captured. A higher bit size results in that an access can be captured later in time, which effectively postpones the refresh further. The least optimal case for postponing the refresh is if the row access occurs a small time interval before the counter is accessed. If a two-bit counter is used the least optimal row access result in that the row is refreshed after $3/4$ of the maximum refresh period. Analogously, a three-bit counter result in that a row is refreshed after minimum $7/8$ of the maximum refresh period.

@@

The technique was simulated on \textit{2~GB} of main memory. Results shows that the refresh reduction was on average $59\%$ and refresh power consumption savings became on average $52\%$. This produced a total DRAM power saving of $12\%$, without any performance degradation.
